---
title: "Exercise 1b"
author: "Santiago Castro Dau"
date: "September 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task
1. Sample 100 values from a log-normal distribution and report the mean and variance of the sample in line in the text.
2. Create a histogram of the distribution and the distribution on the log scale.

### Sub-task No. 1: Sampling
```{r subtask1, echo=TRUE}
# Lets set the seed so the analysisi is reproducible
set.seed(123)

# Input parameters of the distribution
mu <- 0
sigma <- 1

# Now we can use the function rlnorm to sample our data
samp <- rlnorm(n = 100, mu, sigma)

# Now lets print the mean and sd of our sample
mean(samp)
sd(samp)
```

### Sub-task No. 2: Plotting
Now we plot the histogram for our sample in a log scale using the library tidyverse (which imports ggplot2, dplyr and other useful libraries).

```{r subtask2, echo=TRUE, fig.align='center'}
# Import libreries (the have to be previously installed)
suppressMessages(library(tidyverse, warn.conflicts = FALSE))

# Transform samp into a tibble
samp <- samp %>% as_tibble()

# Plot histogram (without log scale)
samp %>% ggplot(aes(x=value)) +
  geom_histogram(binwidth = 0.5, 
                 color = "black",
                 fill = "white",
                 aes(y=..density..)) +
  geom_density(alpha=.2, fill="#FF6666") +
  theme_minimal()

# Plot histogram (without log scale)
samp %>% ggplot(aes(x=value)) +
  geom_histogram(binwidth = 0.5, 
                 color = "black",
                 fill = "white",
                 aes(y=..density..)) +
  geom_density(alpha=.2, fill="#FF6666") +
  scale_x_continuous(trans='log') +
  theme_minimal()

```

